Visualising CHD Pathway Inequalities by ethnicity - DRAFT

### 2024-04-14 draft_report.qmd
Updated text for alteration to calculations

-   The greatest disparity along the CHD pathway is flu vaccinations for patients aged 65+ where the relative index of disparity is 16.70% (95% ci - 16.64%, 16.70%), indicating that 16.7% of activity needs to be redistributed so that rates reflect need.

@@

-   Out of the 33 metrics along the CHD pathway, 10 have an index of disparity of greater than 10%.

@@

|  Cluster  | Number of vaccinations | CHD synthetic prevalence | Rate (No. of vaccinations / CHD synthetic prevalence) | Global rate | Change in number of vaccinations to match global rate |
|:----------:|-----------:|-----------:|:----------:|:----------:|:----------:|
|           |                    *n* |                      *d* |                        *r=n/d*                        | *gr=𝚺n/𝚺d*  |                     *(r-gr) x d*                      |
|     1     |              3,356,002 |                1,026,826 |                         3.27                          |    2.33     |                       -961,239                        |
|     2     |              2,638,698 |                  924,088 |                         2.86                          |    2.33     |                       -483,540                        |
|     3     |              1,862,430 |                  958,825 |                         1.94                          |    2.33     |                       +373,741                        |
|     4     |                476,616 |                  478,728 |                         1.00                          |    2.33     |                       +639,873                        |
|     5     |                332,728 |                  327,542 |                         1.02                          |    2.33     |                       +431,166                        |
| **Total** |          **8,666,474** |            **3,716,009** |                       **2.33**                        |             |                         **0**                         |

>>>>

-   The greatest disparity along the CHD pathway is flu vaccinations for patients aged 65+ where the relative index of disparity is 17.14% (95% ci - 17.11%, 17.17%), indicating that 17.1% of activity needs to be redistributed so that rates reflect need.

@@

-   Out of the 33 metrics along the CHD pathway, 11 have an index of disparity of greater than 10%.

@@

|  Cluster  | Number of vaccinations | CHD synthetic prevalence | Rate (No. of vaccinations / CHD synthetic prevalence) | Global rate | Change in number of vaccinations to match global rate |
|:----------:|-----------:|-----------:|:----------:|:----------:|:----------:|
|           |                    *n* |                      *d* |                        *r=n/d*                        | *gr=𝚺n/𝚺d*  |                     *(gr-r) x d*                      |
|     1     |              3,356,002 |                1,228,453 |                         2.73                          |    1.92     |                      -1,001,284                       |
|     2     |              2,638,698 |                1,124,040 |                         2.35                          |    1.92     |                       -484,121                        |
|     3     |              1,862,430 |                1,181,796 |                         1.58                          |    1.92     |                        402,855                        |
|     4     |                476,616 |                  571,049 |                         0.83                          |    1.92     |                        617,979                        |
|     5     |                332,728 |                  415,950 |                         0.80                          |    1.92     |                        464,571                        |
| **Total** |          **8,666,474** |            **4,521,288** |                         1.92                          |             |                         **0**                         |
